Arbeidskrav våren 2022

### 2022-01-13 MSB106_Arbeidskrav_V22_Backup.Rmd
Muchos Gracias

LQindustri <- syssel_bos %>% 
  select(aar, knavn, Eir_Er_industri) %>% 
  mutate(aar = as.character(aar)) %>% 
  left_join(select(.data = nasjonalt_bosted, aar, Ein_En_Industri), by = c("aar")) %>% 
  mutate(
  andel = Eir_Er_industri/Ein_En_Industri
  )

>>>>

LQindustri <- syssel_bos %>% 
  select(aar, knavn, Eir_Er_industri) %>% 
  mutate(aar = as.character(aar)) %>% 
  left_join(select(.data = nasjonalt_bosted, aar, Ein_En_Industri), by = c("aar")) %>% 
  mutate(
  andel = Eir_Er_industri/Ein_En_Industri
  )
```
